Equivalence Testing and the Second Generation \emph{P}-Value

### 2019-03-09 reply_to_reviews.R1.tex

\def\labelenumi{\arabic{enumi}.}
\item
  We have changed the part of the sentence \enquote{Our conclusions
  about the relationship between TOST \emph{p}-values and SGPV in this
  article are not dependent upon any specific example} into \enquote{Our

@@

  symmetric we can think of the SGPV as a straight line that is directly
  related to the \emph{p}-value from an equivalence test for three
  values} namely p = 0.5 for TOST when the SGPV will be 0.5, and the
  \emph{p}-values for TOST of 0.025 and 0.975 (corresponding to the
  largest observed mean where the SGPV is 0 and the smallest observed
  mean where the SGPV is 1). We have now made it clearer that when we
  talk about \enquote{correspondence between TOST \emph{p}-values and
  the SGPV}, we mean that there is a direct relation between three
  points.

@@

  wanting to express that across the three identified situations, a
  different TOST \emph{p}-value does not imply a different SGPV - the
  SGPV across these ranges of means is aways the same (either 0, 0.5, or
  1) while the TOST \emph{p}-value differs across this range of means.
  We now just directly say what we originally meant, and no longer use
  the word \enquote{unrelated}. For example, \enquote{There are three
  situations where \emph{p}-values for TOST differentiate between
  observed results, while the SGPV does not differentiate.} and
  \enquote{While the SGPV is 1 as long as the confidence interval falls
  completely within the equivalence bounds, the \emph{p}-value for the
  TOST continues to differentiate between results as a function of how
  far the confidence interval lies within the equivalence bounds (the
  further the confidence interval is from both bounds, the lower the

@@

  the SGPV remains stable across a range of observed effects, while the
  TOST \emph{p}-value continues to differentiate, is whenever the CI is
  wider than the equivalence range, and the CI overlaps with the upper
  \emph{and} lower equivalence bound.} We have removed the word
  \enquote{unrelated} throughout the manuscript.

@@

  \enquote{The conclusion of this section on asymmetric confidence
  intervals is that a SGPV of 1 or 0 can still be interpreted as a p
  \textless{} 0:025 or p \textgreater{} 0:975 in an equivalence test,
  since the SGPV and \emph{p}-value for the TOST procedure are always
  directly related at these values.} should no longer be confusing. To
  make the sentence clearer, we have changed \enquote{these values} into

@@

  statement needs to be examined beyond normally distributed data
  requires further examination.}
\item
  We have removed all our earlier statements that the SGPV only works as
  a descriptive statistic. We deleted the sentence \enquote{the SGPV is
  a descriptive statistic (unlike the \emph{p}-value that is calculated

@@

  inferential statistic when interpreted dichotomously. We will leave
  our uncertainty of how specific SGPV values (e.g., SGPV = 0.3) should
  be interpreted to future researchers, and we do not make any
  statements about whether such values are descriptive or inferential.

@@

\section{Reply to Reviewer 2}\label{reply-to-reviewer-2}

Before listing major points, the reviewer raises the point that we
compare SGPV with \emph{p}-values from TOST throughout our paper, and in
all figures, but then at the end, in page 20, we write:

\enquote{Equivalence tests combined with null-hypothesis significance
tests also allow researchers to conclude an effect is significant and
equivalent (i.e., statistically different from zero, but also too small
to be considered meaningful). Thus, the SGPV is used to classify results
into one of three possible categories (with the data falling inside or
outside the equivalence range, or being inconclusive), while equivalence
tests combined with null-hypothesis tests classify results into four
possible categories.}

The reviewer says that \enquote{the authors suddenly switch the premise;
now the SGPV should be replaced by two \emph{p}-values, one from an
equivalence test and one from a NHST}. However, we do not suggest to
replace the SGPV with an equivalence test and a NHST at all. In our
manuscript, we already pointed out how the SGPV is basically the same as
an equivalence test and a minimum effect test (on page 7):

\enquote{The third point where the SGPV and the \emph{p}-value from the
TOST procedure should overlap is where the 95\% CI falls completely
outside of the equivalence range, but one endpoint of the confidence
interval is equal to the equivalence bound (see situation C in Figure
3), when the \emph{p}-value will always be 0.975. Note that this
situation is in essence a minimum-effect test (Murphy, Myors, \& Wolach,
2014). The goal of a minimum-effect is not just to reject a difference
of zero, but to reject the smallest effect size of interest (i.e., the
equivalence bounds). The SGPV summarizes the information from an
equivalence test and a minimum-effect test.}

One might argue that we suggest to replace the SGPV with two tests.
However, the overlap of the TOST \emph{p}-value at 0.975 when SGPV = 0
gives away that the equivalence test can be interpreted as a minimum
effect test against the equivalence bound. When the TOST \emph{p}-value
is 0.975, the 95\% CI touches either the upper or lower equivalence
bound, and fall completely outside of the equivalence range. This is
mathematically identical to a statistically significant minimum effect
test at p \textless{} 0.05. We didn't make this explicit, but we clearly
should have. We have added the sentence (on page 7):

@@

\enquote{An equivalence test and minimum effect test against the same
equivalence bound are complementary, and when a TOST \emph{p}-value is
larger than 0.975, the \emph{p}-value for the minimum effect test is
smaller than 0.05, and the minimum effect test provides no additional
information that can not be derived from the \emph{p}-value from the
equivalence test.}

One might wonder why then, on page 20, why we introduce the idea to
perform both a null-hypothesis significance test and an equivalence
test. We were not clear enough. And indeed, the sentence \enquote{This
interpretation of a SGPV as allowing researchers to reject the null,
reject the presence of a meaningful effect, or remaining inconclusive is
very similar to the Neyman-Pearson interpretation of combining a
null-hypothesis test and an equivalence test} was simply confusing. We
have deleted this sentence and replaced it with \enquote{As already
mentioned, this interpretation of a SGPV as is very similar to the
Neyman-Pearson interpretation of an equivalence test and a minimum
effect tests (which are complementary).} Furthermore, to prevent the
apparent confusion about why we suggested to perform a null-hypothesis
test and equivalence test: part of this confusion was our original
sentence comparing the SGPV and a combination of NHST and an equivalence
test which was not needed, and we understand it made it seem as if SGPV
needs to be replaced by a combination of other tests. But that is not
what we propose. We rewrote the paragraph:

@@

\enquote{Some researchers might be interested in combining an
equivalence tests with a null-hypothesis significance test. This allows
a researcher to ask whether there is an effect that is statistically
different from zero, and whether effect sizes that are considered
meaningful can be rejected. Equivalence tests combined with
null-hypothesis tests classify results into four possible categories,
and for example allow researchers to conclude an effect is significant
and equivalent (i.e., statistically different from zero, but also too
small to be considered meaningful, see (Lakens et al., 2018)).}

We hope this makes it clear we are not pulling a bait and switch. The
SGPV is strongly related to an equivalence test (or it's complement, a
minimum effect test). Describing the relation between the SGPV and TOST
is our main contribution. We just wanted to mention that researchers
might want to combine an equivalence test with a NHST, because in the
literature, this is a question we see many psychologists ask.

We will now discuss the major points in turn.

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\item
  In line with the comments by reviewer 1, in the second paragraph of
  the manuscript we now clearly state: \enquote{We limit our analysis to
  normally distributed continuous data.} After all, \emph{p}-values and
  confidence are directly related, but Bayesian credible intervals would
  not necessarily be, depending on the prior. Blume et al (2018) limit
  their examples to confidence intervals, but explicitly acknowledge
  other possibilities (such as Bayesian intervals). We look forward to
  future papers that illustrate the SGPV with other interval estimates
  and are happy to add the limitation to continuous normally distributed
  data in our article. Note that we did not add that the correspondence
  only holds for situations where the SE's are small compared to the
  width of the equivalence range, as the reviewer suggests.
\item
  The reviewer repeats that the correspondence only holds when SE's are
  small compared to the width of the equivalence range. The
  correspondence is not in the shape of the curve (which clearly differs
  across Figures 2, 6, and 9). We clearly state that: \enquote{When
  confidence intervals are symmetric we can think of the SGPV as a
  straight line that is directly related to the \emph{p}-value from an
  equivalence test for three values.} This correspondence is not
  dependent upon the SE's. It will always hold for continuous normal
  data. The reviewer says that \enquote{The paper does not provide
  theoretical justification for this connection nor any proofs.} We are
  unsure which proof is needed for the overlap between the three points,
  since it is rather trivial and we believe the explanation in the paper
  is very clear.
\end{enumerate}

For the relation between TOST p = 0.5 and SGPV = 0.5, TOST p = 0.025 and
SGPV = 1, and TOST p = 0.975 and SGPV = 1: ``The SGPV is 50\% when the
observed mean falls exactly on the lower or upper equivalence bound,
because 50\% of the symmetrical confidence interval overlaps with the
equivalence range. When the observed mean equals the equivalence bound,
the difference between the mean in the data and the equivalence bound is
0, the \emph{t}-value for the equivalence test is also 0, and thus the
\emph{p}-value is 0.5 (situation A, Figure 3). Two other points always
have to overlap. When the 95\% CI falls completely inside the
equivalence region, and one endpoint of the confidence interval is
exactly equal to one of the equivalence bounds (see situation B in
Figure 3) the TOST \emph{p}-value (which relies on a one-sided test) is
always 0.025, and the SGPV is 1. The third point where the SGPV and the
\emph{p}-value from the TOST procedure should overlap is where the 95\%
CI falls completely outside of the equivalence range, but one endpoint
of the confidence interval is equal to the equivalence bound (see
situation C in Figure 3), when the \emph{p}-value will always be 0.975,
and the SGPV is 0.

We do not think we can provide any other proof for this. A confidence
interval and a \emph{p}-value are directly related. The TOST procedure
is a test using the confidence interval, and the SGPV (now that we
clearly limited our discussion to a SGPV based on a confidence interval
calculated from continuous normal data) compared against the same
equivalence bounds will be related as we describe. But we believe our
article might not have been clear enough about that we limit our
discussion about the correspondence of the curves to these 3 points.
Indeed, in some figures, the curves are less similar (e.g., Figure 6, 9,
13). Nevertheless, in these graphs, we still have the correspondence
between these 3 points (or at least the 2 points if the CI is too wide
compared to the equivalence bounds to ever observe a \emph{p} = 0.025).
To make it clearer that we talk about the overlap in these 3 critical
points, we have added:

\enquote{When we discuss the relationship between the \emph{p}-values
from TOST and the SGPV, we focus on their correspondence at three
values, namely where the TOST \emph{p} = 0.025 and SGPV is 1, where the
TOST \emph{p} = 0.5 and SGPV = 0.5, and where the TOST \emph{p} = 0.975
and SGPV = 1. These three values are important for the SGPV because they
indicate the values at which the SGPV indicates the data should be
interpreted as compatible with the null hypothesis (SGPV = 1), or with
the alternative hypothesis (SGPV = 0), or when the data are strictly
inconclusive (SGPV = 0.5). These three points of overlap are indicated
by the horizontal dotted lines in Figure 2.}

We believe this satisfactorily addresses the point by the reviewer that
\enquote{Because of this lack of discussion, the reader can easily miss
that the close correspondence only occurs when the sample size is large
enough that the standard error is very small relative to the width of
the equivalence zone.} Indeed, the correspondence between the TOST and
SGPV at these 3 points should be obvious to anyone who understands the
relationship between a \emph{p}-value and a confidence interval, so we
do not provide any further proof, but we hope that clarifying we talk
about the correspondence of these 3 points, and not the entire curve, is
sufficient to address point 2.

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\setcounter{enumi}{2}
\item
  We are aware of the Beger and Hsu (1996) article. But if the reviewer
  reads more closely, it should be clear that we never say the TOST is
  UMP. We say that TOST is a test procedure that aims to control error
  rates - our use of the term \enquote{Neyman-Pearson perspective}
  refers to the classic difference between significance tests (Fisher)
  and hypothesis tests (Neyman-Pearson). We do not imply that any test
  that fixes an error rate is a NP test. Because many psychologists are
  not trained in the difference between a Fisherian approach and a
  Neyman Pearson approach to the use of \emph{p}-values, we are simply
  adding a \enquote{Neyman-Pearson} approach in the text to explain that
  \enquote{From a Neyman-Pearson perspective on statistical inferences
  the main conclusion is based on whether or not \(p < \alpha\), and
  thus an equivalence test and SGPV can be performed by simply checking
  whether the confidence interval falls within the equivalence range,
  just as a null-hypothesis test can be performed by checking whether
  the confidence interval contains zero or not.} We believe this is a
  correct use of the term \enquote{Neyman-Pearson perspective on
  statistical inferences}.
\item
  We tried to find the passage the reviewer refers to when he writes
  \enquote{In light of this, the assertion without proof that classical
  \emph{p}-values provide more or better assessments of the
  \enquote{evidence} appear out of place.} but we could not. We do not
  use the word \enquote{evidence} in the text (because neither the
  \emph{p}-value from TOST nor the SGPV are measures of
  \enquote{evidence} - we fully agree with BLume et al., 2018, in this
  respect). We also do not say the \emph{p}-value is \enquote{naturally
  informative}. Indeed, related to point 3 above, we tried to be
  consistent in interpreting the TOST procedure from a Neyman-Pearson
  perspective, and focus on error control. So we regrettably do not know
  how to incorporate this point.
\item
  We fully agree with the reviewer on point 5 that \enquote{The maximum
  Type I Error rate for the SGPV over the null interval is 5\%, exactly
  like the TOST test.} Indeed, given the direct overlap between the TOST
  \emph{p}-value and the SGPV at \emph{p} = 0.025 and 0.0975 and SGPV of
  1 and 0, any error rates (when concluding support for the null or
  alternative when the SGPV is either 1 or 0) must be identical. This is
  why we were so surprised when Blume et al (2018) write \enquote{They
  control the Type I error naturally, forcing it to zero as the sample
  size grows. This, in turn, offsets Type I Error inflation that results
  from multiple comparisons or multiple examinations of accumulating
  data. Findings identified by second-generation \emph{p}-values are
  less likely to be false discoveries than findings identified by
  classical \emph{p}-values. Consequently, second-generation
  \emph{p}-values do not require ad-hoc adjustments to provide strict
  error control and this improves power in studies with massive multiple
  comparisons.} Clearly, it can not both be true that the error rate of
  SGPV and TOST is identical, TOST requires adjusting for multiple
  comparisons, but the SGPV does not.
\end{enumerate}

@@

  not being inferential, thereby solving the issue reviewer 2 raised.
\item
  In line with major point 8, we added information that asymmetric
  confidence intervals around a correlation are symmetric when Fisher

@@

  second-generation \emph{p}-value can vary slightly when the effect
  size scale is transformed. However definitive findings, i.e.~a
  \emph{p}-value of 0 or 1 are \emph{not} affected by the scale
  changes.} We believe this section, although the most detailed, is

@@

  \enquote{significant} does not have the normal language connotation of
  \enquote{important}. We have therefore kept our original sentence.
\end{enumerate}

As a final comment, altough not explicitly listed as a major point of
minor point, we are happy to respond to the reviewers' suggestion that
Perlman and Wu (1999) call for an \enquote{outright ban of TOST}. The
best summary of this discussion (of which Perlman \& Wu is one
contribution) can be found in Meyners (2012), which we cited. The
discussion has different arguments, and Meyners draws the conclusion
that there is no universially preferred approach. The power benefits of
alternative approaches are typically modest, or only noticeable in
situations where all alternatives are underpowered. The power issue is
not that important - the main discussion is about whether equivalence
tests should have a bounded rejection region, like TOST, or an unbounded
rejection region. It might be useful to note that TOST and SGPV are
similar in this respect - both have bounded rejection regions, and if
the reviewer agrees with Perlman and Wu (1999) in the criticism against
TOST, the same criticism applies to the SGPV. If the reviewer reads
Perlman and Wu (1999) as an argument to ban TOST, it is at the same time
an argument to ban the SGPV. We agree with Meyners, who writes:
\enquote{The debate has been quite heated in times; this section intends
to give a brief overview of the debate. We would like to emphasize again
that the differences between the approaches are minor and to a large
extent of academic interest only, as is this debate.} and concludes:
\enquote{To summarize, there is no right or wrong in most of the
arguments; the two opposing parties rather apply different criteria to
select the most appropriate test, one group focusing rather on
mathematical/statistical criteria, the other one more on
interpretability and reasonability.} We have added a reference to this
discussion for the interested reader, and added \enquote{For an
excellent discussion of the strengths and weaknesses of different
frequentist equivalence tests, including alternatives to the TOST
procedure, see Meyners, 2012.}
